Application-Level Regression Testing Framework using Jenkins

### 2017-08-30 manuscript_ccpe/manuscript.tex
Added reference to address comment on evaluation of other tools.
Added ref for IOR config script and watchdog in the text.

These two requirements can be concisely summarized as ``application-level regression testing''. 
Our goal was to implement an automated solution for running these user-level regression tests to evaluate system usability and performance. 
For this purpose we have chosen to use Jenkins \cite{jenkins}.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{IOR-configuration-sample}
\caption{ IOR configuration sample }
\label{fig:IOR-configuration-sample}
\end{figure}
The IOR test is set to run as scheduled by Jenkins with a best-effort through our batch system.
The test synchronously blocks such that the next test will not start until the previous one has completed.
We employ a watchdog script (see Listing \ref{lst:watchdog}) to monitor the batch queue and keep the test active until the system marks it as finished.
This has the side effect of making the minimum test time an integer multiple of the sleep time in the watchdog script.
This may be adjusted to fit individual site needs.
\begin{lstlisting}[frame=tb,captionpos=t,language=bash,caption={pbs/torque watchdog script}, label=lst:watchdog]
#!/bin/bash
echo "=== RUNNING $0 ==="
if [ $# -lt 1 ]
then
  echo "$0: missing argument for jobid"
  exit 1
fi
while true
do
	MYQSTAT=`qstat $1`
	if test "$MYQSTAT" = ""
        then
		echo $1 finished
		exit
	else
		DATE=`date`
		echo "$DATE: waiting for $1 to finish"
	fi
	sleep 5m
done
\end{lstlisting}

>>>>

These two requirements can be concisely summarized as ``application-level regression testing''. 
Our goal was to implement an automated solution for running these user-level regression tests to evaluate system usability and performance. 
For this purpose we have chosen to use Jenkins \cite{jenkins}. (For an evaluation of other tools that may be used for this purpose, see \cite{VergaraLarrea}.)

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{IOR-configuration-sample}
\caption{ IOR configuration sample }
\label{fig:IOR-configuration-sample}
\end{figure}
The IOR test is set to run as scheduled by Jenkins with a best-effort through our batch system. Figure \ref{fig:IOR-configuration-sample} shows sample configuration script for this test. 
The test synchronously blocks such that the next test will not start until the previous one has completed.
We employ a watchdog script (see Listing \ref{lst:watchdog} and its output \ref{fig:IOR-watchdog-out}) to monitor the batch queue and keep the test active until the system marks it as finished.
This has the side effect of making the minimum test time an integer multiple of the sleep time in the watchdog script.
This may be adjusted to fit individual site needs.
\begin{lstlisting}[frame=tb,captionpos=t,language=bash,caption={pbs/torque watchdog script}, label=lst:watchdog]
#!/bin/bash
echo "=== RUNNING $0 ==="
if [ $# -lt 1 ]
then
  echo "$0: missing argument for jobid"
  exit 1
fi
while true
do
	MYQSTAT=`qstat $1`
	if test "$MYQSTAT" = ""
        then
		echo $1 finished
		exit
	else
		DATE=`date`
		echo "$DATE: waiting for $1 to finish"
	fi
	sleep 5m
done
\end{lstlisting}
